Anxiety, avoidance, and sequential evaluation

### 2019-08-01 manuscripts/manuscript/manuscript.tex
almost ready

\begin{figure}[!b]
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../../figures/03_lh.png}}%
  }
  \par \textbf{Figure 4:} A simple deterministic gridworld with two terminal states: one rewarding (blue) and one aversive (red). (B-D, E-G) The development of value expectancies over three steps of learning, for two levels of pessimism.
  States are colored by their value under different levels of pessimism, with arrows showing an optimal trajectory. (B-D) For an optimistic agent ($w=1$), all states (other than the harmful state) take on positive value with learning. (E-G) For a pessimistic agent ($w=0.6$), negative value spreads from the source to antecedent states. As a result of avoidance, the agent learns reward is unobtainable and develops anergic symptoms (i.e. foregoes action). (Parameters: $\gamma = 0.95$)
\end{figure}

@@

\begin{figure}[!b]
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../../figures/05_choice.png}}%
  }
  \par \textbf{Figure 5:} (A) The free choice premium paradigm\cite{Leotti2011,Leotti2014} with equal chance of outcome $R \in [1, -1]$. Non-anxious participants exhibit a preference for the free choice option (blue) despite it conferring no benefit over the fixed choice option (grey). (B) Pessimistic agents show an attenuated free choice bias. The fractional preference for the free choice option over the simulated experiment is shown for three populations of subjects with levels of pessimism $w$ (y-axis; each dot represents an individual simulated agent, and the smoothed density of free choice bias for each pessimism level is also shown.)
  (Parameters: Q-learning with $\gamma = 1.0$, and inverse temperature, $\beta$, increased from 1 to 10 over 100 episodes.)
\end{figure}

>>>>

\begin{figure}[!b]
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../../figures/03_lh.png}}%
  }
  \par \textbf{Figure 4:} A simple deterministic gridworld with two terminal states: one rewarding (blue) and one aversive (red). (B, c) The development of value expectancies over three steps of learning, for two levels of pessimism.
  States are colored by their value under different levels of pessimism, with arrows showing an optimal trajectory. (B) For an optimistic agent ($w=1$), all states (other than the harmful state) take on positive value with learning. (C) For a pessimistic agent ($w=0.6$), negative value spreads from the source to antecedent states. As a result of avoidance, the agent learns reward is unobtainable and develops anergic symptoms (i.e. foregoes action). (Parameters: $\gamma = 0.95$)
\end{figure}

@@

\begin{figure}[t]
  \centerline{%
    \resizebox{1.0\textwidth}{!}{\includegraphics[trim={0 0 0 0},clip]{../../figures/05_choice.png}}%
  }
  \par \textbf{Figure 5:} (A) The free choice premium paradigm\cite{Leotti2011,Leotti2014} with equal chance of outcome $R \in [1, -1]$. Non-anxious participants exhibit a preference for the free choice option (blue) despite it conferring no benefit over the fixed choice option (grey). (B) Pessimistic agents show an attenuated free choice bias. The fractional preference for the free choice option over the simulated experiment is shown for three populations of subjects with levels of pessimism $w$ (y-axis; each dot represents an individual simulated agent, and the smoothed density of free choice bias for each pessimism level is also shown.)
  (Parameters: Q-learning with $\gamma = 1.0$, and inverse temperature, $\beta$, increased from 1 to 10 over 100 episodes.)
\end{figure}
